The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-06 kalman_walk_paper.tex

@@

>>>>

\paragraph{Population isolates and genetic load}
Above we have mostly discussed the case of two separated populations of equal size.
In contrast, consider a small subset of a large population that is suddenly isolated.
It will have a large amount of genetic variance, thanks to its history,
but a small population size -- and so can drift quite quickly until it exhausts its genetic variation.
By this point, it could have accumulated substantial incompatibility with the parental population.
Similarly, in a species with substantial isolation by distance, geographically local systems drift
might lead to genetic load due only to recombination, much as in \citep{phillips1996maintenance}.

@@

This simple quantitative genetics model we use above
has been shown to produce good predictions in many situations,
even when the substantial number of simplifying assumptions are violated \citep{burger1994distribution,turelli1994genetic}.
\plr{the citations are to "on the distribution of the mean and variance" by Burger and Lande; and the "what, me normal" paper of turelli and barton}
The calculations above should be fairly robust even to substantial deviations from normality.
A larger effect on these predictions seems likely due to 
correlations due to molecular constraint, genetic linkage, population structure, historical contingency and so forth.
Although such considerations would not change the qualitative predictions of this model,
their combined effects could substantially change the predicted rate of accumulation of incompatibilities.
